Epilepsy example

### 2022-11-07 src/epil/epil.Rmd
Get nu Laplace marginals working

>>>>

### Using multiple C++ template

Let's just starting by trying to get the Laplace marginals for $\nu$:

```{r}
compile("epil_nu_index.cpp")
dyn.load(dynlib("epil_nu_index"))
```

```{r}
xi_laplace_marginal_nu <- function(i, opt_theta, finegrid) {
  #' To fill
}
```

dat$i <- i

theta_names <- unique(names(opt_theta$par))
map_fixed_theta <- list()

param_fixed_theta <- param

for(theta in theta_names) {
  map_fixed_theta[[theta]] <- rep(factor(NA), length(param[[theta]]))
  param_fixed_theta[[theta]] <- opt_theta$par[names(opt_theta$par) == theta]
}

#' Prepare the initialisation parameters
param_fixed_theta[["nu_i"]] <- param_fixed_theta$nu[i]
param_fixed_theta[["nu_minus_i"]] <- param_fixed_theta$nu[-i]
param_fixed_theta[["nu"]] <- NULL

#' Might need this here if you're getting crashes
# f <- parallel::mcparallel({})
# x <- parallel::mccollect(f)

obj_fixed_theta <- MakeADFun(
  data = dat,
  parameters = param_fixed_theta,
  random = c("nu_minus_i", "epsilon"),
  DLL = "epil_nu_index",
  silent = TRUE,
  map = map_fixed_theta
)

quad <- aghq::aghq(
  ff = obj_fixed_theta,
  k = 3,
  startingvalue = 0,
  control = aghq::default_control_tmb()
)

pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = fine_grid)[[1]]

ggplot(pdf_and_cdf, aes(x = theta, y = pdf)) +
  geom_line() +
  theme_minimal() +
  labs(x = "nu[1]", y = "Posterior")
```

### Using one C++ template
